Measuring Perceptions and Preferences for Meritocracy [^*]

### 2023-05-16 Title Page.Rmd

Juan Carlos Castillo, Department of Sociology, Universidad de Chile *

Luis Maldonado, Institute of Sociology, Pontificia Universidad Católica de Chile

Jorge Atria, Department of Sociology, Universidad Diego Portales

Julio Iturra, Bremen International Graduate School of Social Sciences

Francisco Meneses, Department of Sociology, Universidad de Chile

@@

[^*]: Corresponding author (juancastillov@uchile.cl - [jc-castillo.com](https://juancarloscastillo.github.io/jc-castillo/) -  Ignacio Carrera Pinto 1045 Ñuñoa, Santiago de Chile). The authors recognize the support of ANID/FONDECYT grant 1160921 and of  the Center for Conflict and Social Cohesion Studies (COES)  grant ANID/FONDAP 1513009.

>>>>

Juan Carlos Castillo, Department of Sociology, Universidad de Chile, Santiago de Chile. *

ORCID: 0000-0003-1265-7854

Julio Iturra, Bremen International Graduate School of Social Sciences, Bremen, Germany.

ORCID: 0000-0003-1993-3479

Luis Maldonado, Institute of Sociology, Pontificia Universidad Católica de Chile, Santiago de Chile.

ORCID: 0000-0002-0028-4766

Jorge Atria, Department of Sociology, Universidad Diego Portales, Santiago de Chile.

ORCID: 0000-0001-7145-3048

Francisco Meneses, Department of Sociology, Universidad de Chile, Santiago de Chile.

@@

[^*]: Corresponding author (juancastillov@uchile.cl - [jc-castillo.com](https://juancarloscastillo.github.io/jc-castillo/) -  Ignacio Carrera Pinto 1045 Ñuñoa, Santiago de Chile). The authors recognize the support of ANID/FONDECYT grant 1210847 and of the Center for Conflict and Social Cohesion Studies (COES)  grant ANID/FONDAP 1513009.
